Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-06-16 writing/DraftExposurePaper/DraftExposurePaper.Rmd

```{r echo = FALSE}
library(hurricaneexposure)
```

@@

References {#references .unnumbered}
==========

>>>>

```{r echo = FALSE}
library(hurricaneexposure)
library(knitr)
```

@@

```{r}
studies <- c("Czajkowski 2010", "Rezempour 2014", "Zandbergen 2009", 
             "Currie 2013", "Grabich 2016", "Zaharan 2010", "Kruck 2010", 
             "Villarini 2011", "Atallah 2007")
distance_km <- c("120", "", "Buffer", "25, 30, 60, 75", "30, 60, 100", 
                 "2 counties", "Radial Max Wind", "100-500", "")
rain_mm <- c("", "2/hr, 48/d", "", "", "", "", "", "", "200-500 (Floyd)")
wind_kt <- c("", "", "SSWS", "", "SSWS", "", "34, 50, 64", "", "")
exposure_parameters <- data.frame(studies, distance_km, rain_mm, wind_kt)
kable(exposure_parameters, "markdown")
```
SSWS = Staffir-Simpson Hurricane Wind Scale (TS, 1, 2, 3, 4, and 5). Wind Cutoffs at 34, 64, 83, 96, 113, and 137 kt.  
References {#references .unnumbered}
==========

### 2016-06-16 writing/DraftExposurePaper/DraftExposurePaper.tex

Exposure classification based on rainfall has some advantages. For
example, it allows the identification of exposed counties that are
inland, rather than coastal, but that were affected by heavy rainfall
during the storm. Often, storm-related deaths are associated with inland
flooding. In fact, over half of the hurricane-related fatalities from
1970 to 1999 were a result of freshwater flooding, accounting for the
vast majority of deaths in inland counties ({\textbf{???}}). In another
analysis, researchers found that 79\% of freshwater-drowning fatalities
occured in inland counties,(Czajkowski, Simmons, and Sutter 2011)
further stressing the importance of rainfall in hurricane risk analysis.
Storms can produce a lot of rain especially in certain topographies,
like near mountains, so counties that are well inland can sometimes
experience more extreme rain that other counties at similar distances
from the storm's track.

@@

>>>>

Exposure classification based on rainfall has some advantages. For
example, it allows the identification of exposed counties that are
inland, rather than coastal, but that were affected by heavy rainfall
during the storm. Often, storm-related deaths are associated with inland
flooding. In fact, over half of the hurricane-related fatalities from
1970 to 1999 were a result of freshwater flooding, accounting for the
vast majority of deaths in inland counties (Rappaport 2000). In another
analysis, researchers found that 79\% of freshwater-drowning fatalities
occured in inland counties,(Czajkowski, Simmons, and Sutter 2011)
further stressing the importance of rainfall in hurricane risk analysis.
Storms can produce a lot of rain especially in certain topographies,
like near mountains, so counties that are well inland can sometimes
experience more extreme rain that other counties at similar distances
from the storm's track.

@@

\hypertarget{ref-Rappaport2000}{}
Rappaport, Edward N. 2000. ``Loss of Life in the United States
Associated with Recent Atlantic Tropical Cyclones.'' \emph{Bulletin of
the American Meteorological Society} x: 2065--73.
